---
title: "Personal Project - Data Gaji"
author: "Agnes Septilia"
date: "23/10/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here I’m practicing EDA with the data set of Data Gaji (Salary Data).
Let's start with loading the library and take a look on the dataset.

```{r}
library(tidyverse)
library(dplyr)
library(readxl)
library(scales)
library(descr)

```

```{r}
# take a look on the dataset
salary <- read_xlsx("Data Gaji 2.xlsx")
glimpse(salary)
```

## Task 1 : We want to check whether any duplicate data based on NIP
```{r}
salary %>% count(NIP)
```
## Result on Task 1 : Total data of NIP is equal with total row in dataframe.
So there's no duplicate data (person) on the data.

## Task 2 : Check Turnover rate
```{r}
resign <- salary %>% 
  select(`Masa Perolehan Awal`, `Masa Perolehan Akhir`) %>% 
  mutate(Resigned = ifelse(`Masa Perolehan Akhir` == 12, 0, 1)) %>% 
  group_by(Resigned) %>% 
  count() %>% 
  pull(n)

turnover_rate <- (resign[2] / sum(resign) * 100)
cat(sprintf("Turnover rate is %.0f%s", turnover_rate, '%'))

```

## Task 3 : Make new column PTKP amount

Here's the basic rule of PTKP amount:
- if `Status PTKP` = TK -> 54,000,000
- if `Status PTKP` = K -> 58,500,000
- then add each with `Jumlah Tanggungan` * 4,500,000

```{r}
salary <- salary %>% 
  mutate(PTKP_Amount = ifelse(`Status PTKP` == 'TK', (54000000 + `Jumlah Tanggungan` * 4500000), 
                              (58500000 + `Jumlah Tanggungan` * 4500000))) %>% 
  relocate(PTKP_Amount, .after = `Jumlah Tanggungan`)
glimpse(salary)
```

## Task 4 : Make new column PTKP_to_Bruto, to check whether `Jumlah Penghasilan Bruto` exceed PTKP or not.
The column will have value: 'Under PTKP' if Bruto <= PTKP, and 'Over PTKP' if otherwise.

Note: In real calculation, there will be element of reduction over `Bruto` before it was compared to PTKP. 
But here, we assume the reduction element is none.

```{r}
salary <- salary %>% 
  mutate(PTKP_to_Bruto = ifelse(PTKP_Amount <= `Jumlah Penghasilan Bruto`, 'Under PTKP', 'Over PTKP'))
glimpse(salary)
```

## Task 5 : Single, Married, or Divorced?

Make new column called `Marriage_Status' with below condition:
- if `Status PTKP` == TK and `Jumlah Tanggungan` == 0 -> Then Single
- if `Status PTKP` == K -> Then Married
- if `Status PTKP` == TK and `Jumlah Tanggungan` != 0 -> Then Divorced

Note: Of course, not all TK/1/2/3 are divorced in real life. 
So the category here is only for practice.

```{r}
salary <- salary %>% 
  mutate(Marriage_Status = case_when(`Status PTKP` == 'K' ~ 'Married',
                                     `Status PTKP` == 'TK' & `Jumlah Tanggungan` == 0 ~ 'Single',
                                     TRUE ~ 'Divorced')) %>% 
  relocate(Marriage_Status, .after = `Jumlah Tanggungan`)
glimpse(salary)
```

## Task 6 : How much Single that makes over 100jt per year ?

```{r}
rich_single <- salary %>% 
  filter (Marriage_Status == 'Single', `Jumlah Penghasilan Bruto` > 100000000) %>% 
  count()
cat(sprintf("There are %d person which are single and make over 100million per year", rich_single$n))
```

## Task 7 : Visualize the correlation between gender and salary using Dot Plot
gender -> using column `Jenis Kelamin`
salary -> using column `Gaji Pokok dan Tunjangan Tetap`

```{r}
salary %>% 
  ggplot(aes(x=`Jenis Kelamin`, 
             y = `Gaji Pokok dan Tunjangan Tetap`/1000000, 
             color = `Jenis Kelamin`)) +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 0.5) + 
  labs(title = "Salary distribution based on gender", 
       y = "Fixed Salary in million IDR", 
       x = "Gender", 
       col = "Gender")
```

## Result on Task 7 : 
    - In general, for the same salary amount, there are more female employees than male.
    - Few females get paid higher than the rest of the company.
    
## Task 8 : Check correlation between Gender and Marriage Status using CrossTable

```{r}
CrossTable(x=salary$`Jenis Kelamin`, y=salary$Marriage_Status, prop.c = FALSE, prop.r = TRUE, prop.chisq = FALSE, chisq = TRUE)
```
## Result on Task 8 : p value is less than 0.05 (alpha), so there is correlation between Gender and Marriage Status.
